Classifying Human Driving Behavior via Deep Neural Networks

### 2017-05-30 paper/paper-DrexelFormat.tex
comment

% ####################################################################################################################################
\chapter{Conclusion and Future work}\label{chap:conclusion}
% ####################################################################################################################################
\section{Data Size}
Two different data sizes should be considered on this paper. First data size is number of samples in each traces. Data with more samples in each traces gave better performance from first part of experiments with {\em first model}. The average accuracy with 1 over 10 sampled data show higher accuracy than the average accuracy with 1 over 20 sampled data and 1 over 50 sampled data. From the fact, experiments with more sample, data without re-sampling or data from long driving time, are expected with better performance.

Another data size is the number of traces. All experiments on the paper used 16 traces. The 12 traces were used for training and the 4 traces were used for testing. The 12 traces were not enough to train neural networks: {\em first model}, {\em second model}, and {\em third model}. Especially, {\em second model} and {\em third model} need more data than {\em first model} because two models are more complex than {\em first model}. To train complex neural network needs more data. Next experiments in the future should use data with enough sample in each traces and enough number of traces.

\section{Limitation of Auto-encoder}
The result from experiments with with SAE in {\em second model} and MAE in {\em third model} show bad performance. The principle of AE is to find two matrices: first matrix is used for compression and second matrix is used for decompression. If two matrices are not exist, impossible to reduce original dimensions to target dimensions, either SAE or MAE do not work. For example, during training first layer of MAE in {\em third model} which reduced 98 features to 75 features, error from this was less than 0.009. This is much better performance than reducing 98 dimensions to 25 dimensions. Therefore, the bad performance of AE implies that it is not possible to reduce 98 features of original data to 25 features by AE.

@@

\section{Training Multiple Layer Auto-encoder}
Chapter \ref{subsubsec:MAE} explains how to train MAE based on \cite{hinton2006reducing}. The paper introduces pretraining process, and it can help initialize good weights. However, processing of pretraining takes really long time. For example, average testing time for {\em third model} with 256 neurons took 10 hours and 27 minutes but testing time for {\em second model} with 256 neurons took 8 hours and 33 minutes. The process of pretraining took about 2 hours.

Unlikely train each layer separately in pretraining, add more AE untill it gives big error or it reaches goal dimensions. Figure \ref{fig:train_NMAE1}, Figure \ref{fig:train_NMAE2}, and Figure \ref{fig:train_NMAE3} show how to train MAE.

	Figure \ref{fig:train_NMAE1} shows SAE and its error function is
$$E(\vec{x}, \bold{g_1}(\bold{f_1}(\vec{X}\bold{E_1})\bold{D_1}))$$
Now if it gives small enough error, add one more layer as Figure \ref{fig:train_NMAE2}. In this case, the error function is
$$E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1})\bold{E_2})\bold{D_2})\bold{D_1}))$$
If it also gives small enough error, add one more layer as Figure \ref{fig:train_NMAE3}. In this case, the error function is
$$E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1})\bold{E_2})\bold{E_3})\bold{D_3})\bold{D_2})\bold{D_1}))$$
If it does not give small error, stop adding more layer.

This way can give two benefits. First benefit is to save train time. To compare with method on \cite{hinton2006reducing}, it does not train whole network because this way always train whole network. Another benefit is to find dimensions how much AE can reduce. For the future work, it is worth to compare two different train methods for MAE and find minimize dimensions reduced by AE.

>>>>

% ####################################################################################################################################
\chapter{Conclusion and Future work}\label{chap:conclusion}
% ####################################################################################################################################
\section{Data Size}
Two different data sizes should be considered on this paper. The first data size is the number of samples in each traces. The data with more samples in each traces gave better performance from the first part of experiments with {\em first model}. The average accuracy with 1 over 10 sampled data show a higher accuracy than the average accuracy with 1 over 20 sampled data and 1 over 50 sampled data. From the fact, experiments with more sample, the data without re-sampling or the data from long driving time, are expected with better performance.

Another data size is the number of traces. All experiments on the paper used 16 traces. The 12 traces were used for training and the 4 traces were used for testing. The 12 traces were not enough to train neural networks: {\em first model}, {\em second model}, and {\em third model}. Especially, {\em second model} and {\em third model} need more data than {\em first model} because two models are more complex than {\em first model}. To train complex neural network needs more data. Next experiments in the future should use the data with enough sample in each traces and enough number of traces.

\section{Limitation of Auto-encoder}
The result from experiments with with SAE in {\em second model} and MAE in {\em third model} show the bad performance. The principle of AE is to find two matrices: the first matrix is used for compression and the second matrix is used for decompression. If two matrices are not exist, impossible to reduce original dimensions to the target dimensions, either SAE or MAE do not work. For example, during training the first layer of MAE in {\em third model} which reduced 98 features to 75 features, the error from this was less than 0.009. This is much better performance than reducing 98 dimensions to 25 dimensions. Therefore, the bad performance of AE implies that it is not possible to reduce 98 features of original data to 25 features by AE.

@@

\section{Training Multiple Layer Auto-encoder}
Chapter \ref{subsubsec:MAE} explains how to train MAE based on \cite{hinton2006reducing}. The paper introduces pretraining process, and it can help initializing good weights. However, processing of pretraining takes really long time. For example, average testing time for {\em third model} with 256 neurons took 10 hours and 27 minutes but the testing time for {\em second model} with 256 neurons took 8 hours and 33 minutes. The process of pretraining took about 2 hours.

Unlike training each layer separately in pretraining, add more AE until it gives a big error or it reaches goal dimensions. Figure \ref{fig:train_NMAE1}, Figure \ref{fig:train_NMAE2}, and Figure \ref{fig:train_NMAE3} show how to train MAE.

	Figure \ref{fig:train_NMAE1} shows SAE and its error function is
$$E(\vec{x}, \bold{g_1}(\bold{f_1}(\vec{X}\bold{E_1})\bold{D_1}))$$
Now if it gives small enough error, add one more layer as Figure \ref{fig:train_NMAE2}. In this case, the error function is
$$E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1})\bold{E_2})\bold{D_2})\bold{D_1}))$$
If it gives a small enough error, add one more layer as Figure \ref{fig:train_NMAE3}. In this case, the error function is
$$E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1})\bold{E_2})\bold{E_3})\bold{D_3})\bold{D_2})\bold{D_1}))$$
If it does not give a small error, stop adding more layer.

This way can give two benefits. The first benefit is to save training time. To compare with method on \cite{hinton2006reducing}, it does not train the whole network because this way always train the whole network. Another benefit is to find how much dimensions AE can reduce. For the future work, it is worth comparing two different train methods for MAE and finding minimized dimensions reduced by AE.
